Dynamic Optimization with Particle Swarms (DOPS): A meta-heuristic for parameter estimation in biochemical models

### 2017-12-14 Paper_v7.tex
Working on LATeX issues
adding syblinkski tang ref

\def\includegraphic{}
\def\includegraphics{}

@@

We explored the performance of DOPS if it was permitted to switch between PSO and DDS modes multiple times.
This mode (\texttt{Experimental~DOPS}) performed comparably to DOPS on 10-d Ackley and Rastrigin as well as on 300-dimensional Rastrigin function.
\texttt{Experimental~DOPS} performed better than DOPS on the CHO metabolism problem (Fig. \ref{fig-exp-DOPS-b4}a),
with the average functional value being nearly half of that of DOPS.
To further distinguish DOPS from \texttt{Experimental~DOPS}, we compared the performance of each algorithm on the Eggholder function,
a difficult function to optimize given its its multiple minima.
On the Eggholder function, \texttt{Experimental~DOPS} outperformed DOPS however, neither version of DOPS reached the true minimum at -959.6407 on any trial with a budget of 4,000 function evaluations (Fig. \ref{fig-exp-DOPS-b4}b).
We also explored the performance of both versions of DOPS on the 100 dimensional Styblinksi-Tang function \cite{jamil2013literature} (Fig. \ref{fig-exp-DOPS-b4}c).
In this comparison, \texttt{Experimental~DOPS} significantly outperformed DOPS, finding the true minimum before exhausting its functional evaluation budget, while DOPS does not reach the minimum.
Since the performance of \texttt{Experimental~DOPS} was promising on these problems, we measured its performance on the coagulation problem.
Surprisingly, DOPS performed slightly better than \texttt{Experimental~DOPS} on the coagulation problem (Fig. \ref{fig-exp-DOPS-b4}d);
the final average objective value for DOPS reached 0.9413\% of the initial functional value, compared to 0.9428\% for \texttt{Experimental~DOPS}.

@@

  \begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      A short description of the figure content
      should go here.}
      \end{figure}

>>>>

% \def\includegraphic{}
% \def\includegraphics{}

@@

We explored the performance of DOPS if it was permitted to switch between PSO and DDS modes multiple times.
This mode (\texttt{Experimental~DOPS}) performed comparably to DOPS on 10-d Ackley and Rastrigin as well as on 300-dimensional Rastrigin function.
\texttt{Experimental~DOPS} performed better than DOPS on the CHO metabolism problem (Fig. \ref{fig-exp-DOPS-b4}a),
with the average functional value being nearly half of that of DOPS.
To further distinguish DOPS from \texttt{Experimental~DOPS}, we compared the performance of each algorithm on the Eggholder function,
a difficult function to optimize given its its multiple minima.
On the Eggholder function, \texttt{Experimental~DOPS} outperformed DOPS however, neither version of DOPS reached the true minimum at -959.6407 on any trial with a budget of 4,000 function evaluations (Fig. \ref{fig-exp-DOPS-b4}b).
We also explored the performance of both versions of DOPS on the 100 dimensional Styblinksi-Tang function \cite{styblinski1990experiments} (Fig. \ref{fig-exp-DOPS-b4}c).
In this comparison, \texttt{Experimental~DOPS} significantly outperformed DOPS, finding the true minimum before exhausting its functional evaluation budget, while DOPS does not reach the minimum.
Since the performance of \texttt{Experimental~DOPS} was promising on these problems, we measured its performance on the coagulation problem.
Surprisingly, DOPS performed slightly better than \texttt{Experimental~DOPS} on the coagulation problem (Fig. \ref{fig-exp-DOPS-b4}d);
the final average objective value for DOPS reached 0.9413\% of the initial functional value, compared to 0.9428\% for \texttt{Experimental~DOPS}.

@@
